Computational musicology, ????, Profit

### 2016-07-25 paper.tex
Mention the incompleteness theorem.
Wordsmith the abstract.

\begin{abstract}
In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
literary works. I then apply the theory to devising a program to generate an infinite `copyright infringement song' that contains
all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

Instead, I devised an encoding between the natural numbers and a piece of music. This allowed me to start with the music, encode
it and therefore discover the constant. Playing the Champernowne Constant as music is the reverse process.

>>>>

\begin{abstract}
In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
literary works. I then apply these ideas by devising a program to generate an infinite `copyright infringement song' that contains
all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

Instead, I devised an encoding between the natural numbers and a piece of music, a technique often known as a G{\"o}del numbering
after Kurt G{\"o}del's famous incompleteness theorem. This allowed me to start with the music, encode it and therefore discover the
constant. Playing the Champernowne Constant as music is the reverse process.
